---
title: "Cabbages"
author: "Leilani Guerrero"
date: "Summer2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$: There is no difference between the vitamin C content based on the cultivation methods of c39 and c52  
$H_A$: There is a difference between the vitamin C content based on the cultivation methods of c39 and c52.

# Methods
We are explaining a vitamin c numerical variable by examining the categorical variable cultivation. We will use a T_test to compare the mean of the two vitamin c and cultivation
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(VitC~Cult,data=veggy)
```

The category c39 cultivating cabbages had an overall lower mean for the numerical result of vitamin c. While the c52 category had a higher mean of the vitamin c using their cultivation method. 
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
favstats(VitC~Cult,data=veggy)
```

The cultivation method c39 had a median of 51, while c52 had a median of 64.5. C39 has a mean of 51.5, while c52 has a mean of 64.4. Meaning the cultivation method c52 was more successful in producing a higher average of vitamin c.
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
